Research Spike: Evaluation of Using a Single Mnemonic both for Cryptocurrency and Identity Wallets

### 2021-12-16 prism-backend/research/single-mnemonic/bip32-etal.tex
Added some extra descriptions on BIP44 and Cardano & Atala variations.

\paragraph{Lightwallet.}

\paragraph{Atala.}

>>>>

\paragraph{Lightwallet.} HD wallets in Cardano are mostly BIP44-compatible
wallets, with the exception that the used elliptic curve is Ed25519 \needcite,
instead of Secp256k1 \needcite, like Bitcoin's BIP32 (and thus, BIP44). This
difference is marked by using index 1852 for hardened child derivation at
layer 1 (purpose level), as specified in CIP1852%
\footnote{\url{https://cips.cardano.org/cips/cip1852/}. Last access, December
  15th, 2021.}.

\paragraph{Atala.} HD wallets in Atala follow a slightly different tree
organisation, layer-wise. Namely, it defines 4 layers: root, DID number, key
type, and index. All child derivations are done in hardened mode. The elliptic
curve is Secp256k1, as BIP44. See the key derivation document for details%
\footnote{\url{https://github.com/input-output-hk/atala-prism/blob/master/prism-backend/docs/protocol/key-derivation.md}. Last access December 15th, 2021. \textbf{WARNING!
    Internal link!}}.
